---
title: "Sponge_seurat_clean"
output: html_document
date: "2024-04-02"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(Seurat)
library(ggplot2)
library(cowplot)
library(DoubletFinder)
library(harmony)
```
```{r}
dataset_loc <- "/tank/projects/Zubarev_sponge/Analysis/2024_01_02_CellRanger/"
ids <- c("bob_1", "bob_2")

d10x.data <- sapply(ids, function(i){
  d10x <- Read10X(file.path(dataset_loc,i,"/outs/filtered_feature_bc_matrix/"))
  colnames(d10x) <- paste(sapply(strsplit(colnames(d10x),split="-"),'[[',1L),i,sep="-")
  d10x
})
```

Create two Seurat objects

```{r}
seurat_list<-sapply(d10x.data, function(i){CreateSeuratObject(i,
  project = "H. dujardini cell atlas", 
  min.cells = 10,
  min.features = 200,
  names.field = 2,
  names.delim = "_")})
```

Calculate mito genes percentage

```{r}
mito.genes<-grep("^MT-", c(rownames(seurat_list$bob_1), colnames(seurat_list$bob_2)), value = T)
mito<-sapply(seurat_list, function(i){i[mito.genes, ]})

percent.mito.bob1 <- Matrix::colSums(mito$bob_1@assays$RNA) / Matrix::colSums(seurat_list$bob_1@assays$RNA)
seurat_list$bob_1 <- AddMetaData(
  object = seurat_list$bob_1,
  metadata = percent.mito.bob1,
  col.name= "percent.mito")

percent.mito.bob2 <- Matrix::colSums(mito$bob_2@assays$RNA) / Matrix::colSums(seurat_list$bob_2@assays$RNA)
seurat_list$bob_2 <- AddMetaData(
  object = seurat_list$bob_2,
  metadata = percent.mito.bob2,
  col.name= "percent.mito")
```

```{r}
pdf("/tank/projects/Zubarev_sponge/Analysis/2024_05_18_Seurat_clean/Vln_mito_nofilter.pdf")
VlnPlot(seurat_list$bob_1, features = c("nFeature_RNA", "nCount_RNA", "percent.mito"), ncol = 3)
VlnPlot(seurat_list$bob_2, features = c("nFeature_RNA", "nCount_RNA", "percent.mito"), ncol = 3)
dev.off()
```

Filter out cells with high mito genes percentage

```{r}
seurat_list<-sapply(seurat_list, function(i){subset(i, subset = nFeature_RNA > 200 & percent.mito < 0.05)})
```

The same plots after the filtering

```{r}
pdf("/tank/projects/Zubarev_sponge/Analysis/2024_05_18_Seurat_clean/Vln_mito_filter.pdf")
VlnPlot(seurat_list$bob_1, features = c("nFeature_RNA", "nCount_RNA", "percent.mito"), ncol = 3)
VlnPlot(seurat_list$bob_2, features = c("nFeature_RNA", "nCount_RNA", "percent.mito"), ncol = 3)
dev.off()
```

Pre-processing for DoubletFinder: normalization, variable genes selection, data scaling, PCA

```{r}
seurat_list<-sapply(seurat_list, function(i){
i <- NormalizeData(i, normalization.method = "LogNormalize", scale.factor = 10000)
i <- FindVariableFeatures(i, selection.method = "vst", nfeatures = 2000)
all.genes<-rownames(i)
i <- ScaleData(i, features = all.genes)
i <- RunPCA(i, features = VariableFeatures(object = i))
return(i)
})
```

```{r}
#pdf("/tank/projects/Zubarev_sponge/Analysis/2024_05_18_Seurat_clean/Elbow.pdf")
ElbowPlot(seurat_list$bob_1)
ElbowPlot(seurat_list$bob_2)
#dev.off()
```

Clusterize cells

```{r}
seurat_list<-sapply(seurat_list, function(i){
i <- FindNeighbors(i, dims = 1:50)
i <- FindClusters(i, resolution = 0.25)
i <- RunUMAP(i, dims = 1:50)
return(i)
})
```

```{r}
DimPlot(seurat_list$bob_1, reduction = "umap", label=TRUE, label.size=3)
DimPlot(seurat_list$bob_2, reduction = "umap", label=TRUE, label.size=3)
```


```{r}
## pK Identification (no ground-truth) ------------------------------------------------------------
sweep.res.list_bob1 <- paramSweep(seurat_list$bob_1, PCs = 1:30, sct = FALSE)
sweep.stats_bob1 <- summarizeSweep(sweep.res.list_bob1, GT = FALSE)
bcmvn_bob1 <- find.pK(sweep.stats_bob1)
```

```{r}
## Homotypic Doublet Proportion Estimate ------------------------------------------------------------
homotypic.prop <- modelHomotypic(seurat_list$bob_1@meta.data$seurat_clusters)           ## ex: annotations <- seu_kidney@meta.data$ClusteringResults
nExp_poi <- round(0.075*nrow(seurat_list$bob_1@meta.data))  ## Assuming 7.5% doublet formation rate - tailor for your dataset
nExp_poi.adj_bob1 <- round(nExp_poi*(1-homotypic.prop))
```

```{r}
bob1_doublet_cleaned <- doubletFinder(seurat_list$bob_1, PCs = 1:30, pN = 0.25, pK = 0.13, nExp = nExp_poi.adj_bob1, reuse.pANN = FALSE, sct=FALSE)
```

```{r}
## pK Identification (no ground-truth) ------------------------------------------------------------
sweep.res.list_bob2 <- paramSweep(seurat_list$bob_2, PCs = 1:30, sct = FALSE)
sweep.stats_bob2 <- summarizeSweep(sweep.res.list_bob2, GT = FALSE)
bcmvn_bob2 <- find.pK(sweep.stats_bob1)
```

```{r}
## Homotypic Doublet Proportion Estimate ------------------------------------------------------------
homotypic.prop <- modelHomotypic(seurat_list$bob_2@meta.data$seurat_clusters)           ## ex: annotations <- seu_kidney@meta.data$ClusteringResults
nExp_poi <- round(0.075*nrow(seurat_list$bob_2@meta.data))  ## Assuming 7.5% doublet formation rate - tailor for your dataset
nExp_poi.adj_bob2 <- round(nExp_poi*(1-homotypic.prop))
```


```{r}
bob2_doublet_cleaned <- doubletFinder(seurat_list$bob_2, PCs = 1:30, pN = 0.25, pK = 0.13, nExp = nExp_poi.adj_bob2, reuse.pANN = FALSE, sct=FALSE)
```

Add "replicate" metadata column

```{r}
bob1_doublet_cleaned@meta.data$replicate <- "bob1"
bob2_doublet_cleaned@meta.data$replicate <- "bob2"
```

Draw doublets

```{r}
pdf("/tank/projects/Zubarev_sponge/Analysis/2024_05_18_Seurat_clean/Doublets_UMAP.pdf")
DimPlot(bob1_doublet_cleaned, reduction = "umap", label=TRUE, group.by = "DF.classifications_0.25_0.13_644", label.size=3)
DimPlot(bob2_doublet_cleaned, reduction = "umap", label=TRUE, group.by = "DF.classifications_0.25_0.13_775", label.size=3)
dev.off()
```

Draw mito genes %

```{r}
pdf("/tank/projects/Zubarev_sponge/Analysis/2024_05_18_Seurat_clean/Mito_UMAP.pdf")
FeaturePlot(bob1_doublet_cleaned, features="percent.mito")
FeaturePlot(bob2_doublet_cleaned, features="percent.mito")
dev.off()
```


```{r}
bob1_doublet_cleaned<-subset(bob1_doublet_cleaned, subset = DF.classifications_0.25_0.13_644 == "Singlet")
bob2_doublet_cleaned<-subset(bob2_doublet_cleaned, subset = DF.classifications_0.25_0.13_775 == "Singlet")
```

Concatenate objects

```{r}
experiment.aggregate<-merge(bob1_doublet_cleaned, bob2_doublet_cleaned, merge.dr=FALSE, project="Halisarca dujardinii cell atlas")
```

Basic preprocessing

```{r}
experiment.aggregate <- NormalizeData(experiment.aggregate, normalization.method = "LogNormalize", scale.factor = 10000)
experiment.aggregate <- FindVariableFeatures(experiment.aggregate, selection.method = "vst", nfeatures = 2000)
all.genes<-rownames(experiment.aggregate)
experiment.aggregate <- ScaleData(experiment.aggregate, features = all.genes)
experiment.aggregate <- RunPCA(experiment.aggregate, features = VariableFeatures(object = experiment.aggregate))
```

Apply Harmony integration algorithm

```{r}
experiment.aggregate<-RunHarmony(experiment.aggregate, group.by.vars="replicate", nclust = 50, max_iter = 10, reduction.use="pca")
```

Basic preprocessing on Harmony dimension reduction. Use high resolution to separate all small clusters.

```{r}
experiment.aggregate <- experiment.aggregate %>%
    FindNeighbors(reduction = "harmony", dims=1:50) %>%
    FindClusters(resolution = 0.85)
experiment.aggregate <- experiment.aggregate %>%
    RunUMAP(reduction = "harmony",  dims = 1:50)
```

```{r}
pdf("/tank/projects/Zubarev_sponge/Analysis/2024_05_18_Seurat_clean/Harmony_UMAP.pdf", width=10, height=5)
DimPlot(experiment.aggregate, reduction = "umap", label=TRUE, label.size=4, split.by = "replicate")
dev.off()
```

```{r}
pdf("/tank/projects/Zubarev_sponge/Analysis/2024_05_18_Seurat_clean/Harmony_UMAP_drop.pdf", width=7, height=7)
DimPlot(experiment.aggregate, reduction = "umap", label=TRUE, label.size=3)
dev.off()
```

Remove small cell populations without clear markers (can be proven with code to obtain and annotate markers below, but not included here).

```{r}
experiment.aggregate<-subset(experiment.aggregate, subset = (seurat_clusters!="19")&(seurat_clusters!="22")&(seurat_clusters!="29")&(seurat_clusters!="30")&(seurat_clusters!="33")&(seurat_clusters!="34"))
```

Not very clean, but it will be more clean with marker-based reclustering.

```{r}
DimPlot(experiment.aggregate, reduction = "umap", label=TRUE, label.size=2, split.by = "replicate")
```

With lower resolution

```{r}
experiment.aggregate <- experiment.aggregate %>%
    FindNeighbors(reduction = "harmony", dims=1:50) %>%
    FindClusters(resolution = 0.3)
#experiment.aggregate <- experiment.aggregate %>%
#    RunUMAP(reduction = "harmony",  dims = 1:50)
```

```{r}
DimPlot(experiment.aggregate, reduction = "umap", label=TRUE, label.size=2, split.by = "replicate")
```

## Marker genes search and annotation

```{r}
markers_batchcorrected<-FindAllMarkers(experiment.aggregate, logfc.threshold = 0.1)
```

Filter and sort marker table

```{r}
markers_batchcorrected<-markers_batchcorrected[(markers_batchcorrected$avg_log2FC > 0.1) & (markers_batchcorrected$p_val_adj < 1e-50),]
markers_batchcorrected<-markers_batchcorrected[order(markers_batchcorrected$avg_log2FC, decreasing = TRUE),]
markers_batchcorrected<-markers_batchcorrected[order(markers_batchcorrected$cluster, decreasing = FALSE),]
```

Read annotations

```{r}
#Trinotate
trinotate <- read_xlsx('/tank/projects/Zubarev_sponge/Analysis/2024_01_06_Seurat/Trinotate_annotation_report.xlsx')
colnames(trinotate)[1] <- 'gene'
#Remove some redundant transcripts/isoforms of genes, which names are written like "HD_13401-RA.1.656e5673"
trinotate <- trinotate[!grepl("RA.", trinotate$transcript_id),]
```

```{r}
#eggNOG-mapper
emapper<-read_excel("/tank/projects/Zubarev_sponge/Analysis/2024_02_20_eggNOG_mapper/out.emapper.annotations_nocomments.xlsx")
colnames(emapper)[1]<-"prot_id"
```

```{r}
#manual annotation of some genes provided by Institute of Developmantal Biology RAS
idb_ras<-read_excel("/tank/projects/Zubarev_sponge/Analysis/2024_01_06_Seurat/Sc_Marker clasters_IDB_RAS.xls")
colnames(idb_ras)[3]<-"transcript_id"
```

Annotate markers by joining all annotations, gather all ID variants in the first columns

```{r}
markers_annotated <- markers_batchcorrected %>% left_join(trinotate, by='gene') %>% left_join(emapper, by="prot_id") %>% left_join(idb_ras, by="transcript_id")

markers_annotated <- markers_annotated[,c(6:8,11,1:5,9,10,12:45)]
```

Filter out markers expressed at low fraction of cluster cells. Retain only markers expressed at 1/2 cluster cells or more.

```{r}
markers_annotated<-markers_annotated[markers_annotated$pct.1 > 0.2,]
```

If one gene is a marker for several clusters, retain the record with maximium logFC. As well, retain only the most useful columns.

```{r}
markers_summary<- markers_annotated %>% group_by(transcript_id, gene) %>% summarise(max_log2FC=max(avg_log2FC), cluster=cluster[which.max(avg_log2FC)], Blastp=sprot_Top_BLASTP_hit[which.max(avg_log2FC)], Emapper_PFAMs=PFAMs[which.max(avg_log2FC)], Name=name[which.max(avg_log2FC)])

markers_summary<-arrange(markers_summary, cluster, desc(max_log2FC))
```

Retain top30

```{r}
markers_top100 <- markers_summary %>% group_by(cluster) %>% group_modify(~head(.x,n=100))
ungroup(markers_top100)
```

```{r}
markers_top30 %>% group_by(cluster) %>% summarise(maxFC=max(max_log2FC))
```

Draw pictures of marker expression - top30 per cluster. (One PDF will contain markers for one cluster, to avoid too heavy PDFs.) Time-consuming (~1 hour) since will draw hundreds of plots.

```{r}
for (j in c(0:19))
{
j<-as.character(j)
print(paste0("Plotting cluster ", j))

#subset one cluster from a table
onecluster<-markers_top30[markers_top30$cluster==j,]

filename<-paste0("/tank/projects/Zubarev_sponge/Analysis/2024_04_04_Seurat_Harmony/markers_0.7_31clust/Markers_expression_07_31c_cluster",j,".pdf")
pdf(file=filename, onefile = TRUE)

for (i in 1:dim(onecluster)[1])
{

if (!is.na(onecluster$transcript_id[i]))
{
#extract name from different sources of annotation. Names extracted in order IDB RAS > BLASTP.
if (!is.na(onecluster$Name[i])) {fullname=str_trunc(onecluster$Name[i], 45, ellipsis = "...")} else if (onecluster$Blastp[i]==".") {fullname="Unknown"} else {fullname=strsplit(strsplit(onecluster$Blastp[i],"\\^")[[1]][6], "=")[[1]][2]}

#make plot
plot<-FeaturePlot(experiment.aggregate, features = onecluster$gene[i], label=TRUE, label.size=3)+theme(plot.title=element_text(size=12), axis.text=element_text(size=12), axis.title=element_text(size=12),plot.caption = element_text(size=12))+labs(title = paste0(onecluster$transcript_id[i]," | ", onecluster$gene[i]," | ",str_trunc(fullname, 45, ellipsis = "...")), caption = paste0("Marker of Cluster ",onecluster$cluster[i]," with log2FC = ",round(onecluster$max_log2FC[i], digits=5),"."))
#ggsave(filename="/tank/projects/Zubarev_sponge/Analysis/2024_01_06_Seurat/Markers_expression_UMAPS_for_IDB.pdf", device = "pdf")
print(plot)
}
}
dev.off()
}
```

```{r}
saveRDS(markers_summary, '/tank/projects/Zubarev_sponge/Analysis/2024_03_28_Celltype_deconvolution/markers_top_v20240405.rds')
```

```{r}
write.table(as.matrix(GetAssayData(object = experiment.aggregate, slot = "counts")), 
            '/tank/projects/Zubarev_sponge/Analysis/2024_04_04_SCENIC/sponge_count_matrix.csv', 
            sep = ',', row.names = T, col.names = T, quote = F)
```

```{r}
#This is needed for scGate
experiment.aggregate <- JoinLayers(experiment.aggregate)
```

There object can be restored from the saved version.

```{r}
```

## Marker-based reclustering

```{r}
library(scGate)
```

Best markers list was obtained by manual inspection of expression maps.
Perform marker-based reclustering.

```{r}
Cluster0_model <- gating_model(name = "0&Transition cell", signature = c("nbis-gene-14338+", "nbis-gene-2643+", "nbis-gene-2878-", "nbis-gene-27678-"))
#Note the correct dashes in the names!!! Long and short dashes are the different symbols...
Cluster1_model<-gating_model(name = "Cluster_1", signature = c(" nbis-gene-3245+", "nbis-gene-7566+"))
Cluster2_model<-gating_model(name = "Proliferating", signature = c("nbis-gene-4339+", "nbis-gene-12146+"))
#11783 
Cluster3_model<-gating_model(name = "Cluster_3", signature = c("nbis-gene-12457+", "nbis-gene-5418"))
Cluster4_model<-gating_model(name = "Cluster_4", signature = c("nbis-gene-2548", " nbis-gene-3067", "nbis-gene-27301")) #very unique expression pattern, many clear markers
Cluster5_model<-gating_model(name = "Cluster_5", signature = c("nbis-gene-9784", "nbis-gene-26036"))
#26036, 24371
Cluster6_model<-gating_model(name = "Cluster_6", signature = c("nbis-gene-4492", "nbis-gene-20686")) #not easy, it's better without 2nd marker
Cluster7_model<-gating_model(name = "Cluster_7", signature = c("nbis-gene-10124", "nbis-gene-10142"))
Cluster8_model<-gating_model(name = "Cluster_8", signature = c("nbis-gene-125", "nbis-gene-12389")) #not well separated from cluster 3, markers are common in some cases.
Cluster9_model<-gating_model(name = "Cluster_9", signature = c("nbis-gene-5002", "nbis-gene-6478", "nbis-gene-2309"))
Cluster10_model<-gating_model(name = "Cluster_10", signature = c("nbis-gene-9214", "nbis-gene-9213", "nbis-gene-9210")) #very well-separated
Cluster11_model<-gating_model(name = "Cluster_11", signature = c("nbis-gene-5806", "nbis-gene-1749")) #
Cluster12_model<-gating_model(name = "Cluster_12", signature = c("nbis-gene-1890", "nbis-gene-3273")) 
#baseline level of marker expression exists. 1890, 3273
Cluster13_model<-gating_model(name = "Cluster_13", signature = c("nbis-gene-12799", "nbis-gene-13877"))
Cluster14_model<-gating_model(name = "Cluster_14", signature = c("nbis-gene-24995", " nbis-gene-7451")) #good
#Cluster15_model<-gating_model(name = "Cluster_15", signature = c("")) #unclear
Cluster16_model<-gating_model(name = "Cluster_16", signature = c("nbis-gene-20174", "nbis-gene-11670"))
Cluster17_model<-gating_model(name = "Cluster_17", signature = c("nbis-gene-2826", "nbis-gene-2824")) #good
Cluster18_model<-gating_model(name = "Cluster_18", signature = c("nbis-gene-8546", "nbis-gene-8580")) #good
Cluster19_model<-gating_model(name = "Cluster_19", signature = c("nbis-gene-20493", "nbis-gene-4284")) #very good
Cluster20_model<-gating_model(name = "Cluster_20", signature = c("nbis-gene-18675", "nbis-gene-6290")) #acceptable, drop candidate

Cluster21_model<-gating_model(name = "Cluster_21", signature = c("nbis-gene-10143", "nbis-gene-10144"))
Cluster22_model<-gating_model(name = "Cluster_22", signature = c("nbis-gene-3963"))
#clusters 22-24 dropped.
```

```{r}
model_list<-list("cluster0"=Cluster0_model, 
                 "cluster1"=Cluster1_model, 
                 "cluster2"=Cluster2_model, 
                 "cluster3"=Cluster3_model, 
                 "cluster4"=Cluster4_model,
                 "cluster5"=Cluster5_model, 
                 "cluster6"=Cluster6_model, 
                 "cluster7"=Cluster7_model, 
                 "cluster8"=Cluster8_model, 
                 "cluster9"=Cluster9_model,
                 "cluster10"=Cluster10_model, 
                 "cluster11"=Cluster11_model,
                 "cluster12"=Cluster12_model,
                 "cluster13"=Cluster13_model, 
                 "cluster14"=Cluster14_model, 
                 "cluster16"=Cluster16_model, 
                 "cluster17"=Cluster17_model, 
                 "cluster18"=Cluster18_model, 
                 "cluster19"=Cluster19_model,
                 "cluster20"=Cluster20_model, 
                 "cluster21"=Cluster21_model,
                 "cluster22"=Cluster22_model)
obj <- scGate(data = experiment.aggregate, model = model_list, verbose = T, reduction = "harmony", ncores=20)
```

```{r}
obj@meta.data %>% count(scGate_multi)
```

```{r}
#pdf(file="/tank/projects/Zubarev_sponge/Analysis/2024_03_06_scGate_and_manual_annotation/19clusters_model.pdf")
DimPlot(obj, group.by = "scGate_multi", label=TRUE, repel=TRUE)
#dev.off()
```

```{r}
obj<-subset(obj, subset = scGate_multi != "Multi")
```

```{r}
DimPlot(obj, group.by = "scGate_multi", label=TRUE, repel=TRUE)
```

```{r}
FeaturePlot(obj, features=c("nbis-gene-25113", "nbis-gene-14106","nbis-gene-24502","nbis-gene-3672"))
```

```{r}
obj <- DietSeurat(obj, counts = TRUE, 
  data = TRUE, 
  scale.data = FALSE, 
  features = rownames(obj), 
  assays = "RNA",
  dimreducs = NULL,
  graphs = NULL,
  misc = TRUE)
```

Clusters 19 and 21 does not have a lot of good markers. Exclude them from deconvolution analysis

```{r}
obj<-subset(obj, subset = (scGate_multi!="cluster21")&(scGate_multi!="cluster22"))
```

```{r}
saveRDS(obj, '/tank/projects/Zubarev_sponge/Analysis/2024_03_28_Celltype_deconvolution/HDuj_nodoublets_harmony_scGate_multi_removed_v20240404.rds')
```

```{r}
library(SeuratDisk)
library(tidyr)
library(dplyr)
```

### Renumeration, annotation and final pictures

```{r}
HDuj_all<-LoadH5Seurat("/tank/projects/Zubarev_sponge/Analysis/2024_04_04_Seurat_Harmony/Harmony_scGate_NA_Multi_present.h5Seurat")
HDuj_cluster0<-LoadH5Seurat("/tank/projects/Zubarev_sponge/Analysis/2024_04_04_Seurat_Harmony/Cluster0_11subclusters.h5Seurat")
```

```{r}
model_list<-list("cluster0"=Cluster0_model, 
                 "cluster1"=Cluster1_model, 
                 "cluster2"=Cluster2_model, 
                 "cluster3"=Cluster3_model, 
                 "cluster4"=Cluster4_model,
                 "cluster5"=Cluster5_model, 
                 "cluster6"=Cluster6_model, 
                 "cluster7"=Cluster7_model, 
                 "cluster8"=Cluster8_model, 
                 "cluster9"=Cluster9_model,
                 "cluster10"=Cluster10_model, 
                 "cluster11"=Cluster11_model,
                 "cluster12"=Cluster12_model,
                 "cluster13"=Cluster13_model, 
                 "cluster14"=Cluster14_model, 
                 "cluster15"=Cluster16_model, 
                 "cluster16"=Cluster17_model, 
                 "cluster17"=Cluster18_model, 
                 "cluster18"=Cluster19_model,
                 "cluster19"=Cluster21_model,
                 "cluster20"=Cluster22_model)
HDuj_all <- scGate(data = HDuj_all, model = model_list, verbose = T, reduction = "harmony", ncores=20)
```

```{r}
pdf("/tank/projects/Zubarev_sponge/Analysis/2024_05_18_Seurat_clean/UMAP_multi_present_clusters_renumbered.pdf", width=8, height=7)
DimPlot(HDuj_all, group.by = "scGate_multi", label = TRUE, label.size = 5, repel=TRUE)
dev.off()
```

```{r}
HDuj_no_multi<-subset(HDuj_all, subset=(scGate_multi != "Multi"))
```

```{r}
#pdf("/tank/projects/Zubarev_sponge/Analysis/2024_05_18_Seurat_clean/UMAP_multi_discarded_clusters_renumbered.pdf", width=8, height=7)
DimPlot(HDuj_no_multi, group.by = "scGate_multi", label = TRUE, label.size = 5, repel=TRUE)
#dev.off()
```
Save H5Seurat and h5ad objects

```{r}
HDuj_all[["RNA3"]] <- as(object = HDuj_all[["RNA"]], Class = "Assay")
DefaultAssay(HDuj_all) <- "RNA3"
HDuj_all[["RNA"]] <- NULL
HDuj_all <- RenameAssays(object = HDuj_all, RNA3 = 'RNA')
```

```{r}
SaveH5Seurat(HDuj_all, filename = "/tank/projects/Zubarev_sponge/Analysis/2024_05_18_Seurat_clean/HDuj_reclustered_renumbered_20240522.h5Seurat")
Convert("/tank/projects/Zubarev_sponge/Analysis/2024_05_18_Seurat_clean/HDuj_reclustered_renumbered_20240522.h5Seurat", dest="h5ad")

```
Make and save an object for deconvolution (without 2 last clusters, cluster 0 and 2 unified).

```{r}
HDuj_deconv<-subset(HDuj_no_multi, subset=(scGate_multi != "cluster20")&(scGate_multi != "cluster19"))
HDuj_deconv@meta.data$scGate_multi[HDuj_deconv@meta.data$scGate_multi == 'cluster0']<-'cluster0_2'
HDuj_deconv@meta.data$scGate_multi[HDuj_deconv@meta.data$scGate_multi == 'cluster2']<-'cluster0_2'
```

```{r}
cluster0_annot<-HDuj_cluster0@meta.data[c("seurat_clusters")]
colnames(cluster0_annot)<-"cluster0_subcluster"
cluster0_annot$cellID<-rownames(cluster0_annot)
```

```{r}
cells_annot_all<-HDuj_all@meta.data
```

```{r}
cells_annot_all$cellID<-rownames(cells_annot_all)
```

```{r}
cells_annot_all<- left_join(cells_annot_all, cluster0_annot, by="cellID")
```

```{r}
rownames(cells_annot_all)<-cells_annot_all$cellID
```


```{r}
cells_annot_all$cell_type<-"Multi"
cells_annot_all$cell_type[cells_annot_all$scGate_multi=="cluster1"]<-"Cluster_1"
cells_annot_all$cell_type[cells_annot_all$cluster0_subcluster==1]<-"Archaeocytes"
cells_annot_all$cell_type[cells_annot_all$cluster0_subcluster==6]<-"Archaeocytes"
cells_annot_all$cell_type[cells_annot_all$cluster0_subcluster==8]<-"Archaeocytes"
cells_annot_all$cell_type[cells_annot_all$cluster0_subcluster==2]<-"Choanocytes"
cells_annot_all$cell_type[cells_annot_all$cluster0_subcluster==3]<-"Choanocytes"
cells_annot_all$cell_type[cells_annot_all$scGate_multi=="cluster2"]<-"Choanoblasts"
cells_annot_all$cell_type[cells_annot_all$scGate_multi=="cluster3"]<-"Pinacocytes_1"
cells_annot_all$cell_type[cells_annot_all$scGate_multi=="cluster4"]<-"Mesohyl_cells_1"
cells_annot_all$cell_type[cells_annot_all$scGate_multi=="cluster5"]<-"Pinacocytes_2"
cells_annot_all$cell_type[cells_annot_all$scGate_multi=="cluster6"]<-"Cluster_6"
cells_annot_all$cell_type[cells_annot_all$scGate_multi=="cluster7"]<-"Cluster_7"
cells_annot_all$cell_type[cells_annot_all$scGate_multi=="cluster8"]<-"Pinacocytes_3"
cells_annot_all$cell_type[cells_annot_all$scGate_multi=="cluster9"]<-"Mesohyl_cells_2"
cells_annot_all$cell_type[cells_annot_all$scGate_multi=="cluster10"]<-"Pinacocytes_4"
cells_annot_all$cell_type[cells_annot_all$scGate_multi=="cluster11"]<-"Cluster_11"
cells_annot_all$cell_type[cells_annot_all$scGate_multi=="cluster12"]<-"Cluster_12"
cells_annot_all$cell_type[cells_annot_all$scGate_multi=="cluster13"]<-"Cluster_13"
cells_annot_all$cell_type[cells_annot_all$scGate_multi=="cluster14"]<-"Cluster_14"
cells_annot_all$cell_type[cells_annot_all$scGate_multi=="cluster15"]<-"Cluster_15"
cells_annot_all$cell_type[cells_annot_all$scGate_multi=="cluster16"]<-"Cluster_16"
cells_annot_all$cell_type[cells_annot_all$scGate_multi=="cluster17"]<-"Cluster_17"
cells_annot_all$cell_type[cells_annot_all$scGate_multi=="cluster18"]<-"Cluster_18"
cells_annot_all$cell_type[cells_annot_all$scGate_multi=="cluster19"]<-"Cluster_19"
cells_annot_all$cell_type[cells_annot_all$scGate_multi=="cluster20"]<-"Cluster_20"
cells_annot_all$cell_type[cells_annot_all$scGate_multi=="NA"]<-"NA"
```

```{r}
HDuj_all@meta.data<-cells_annot_all
```

```{r}
pdf('/tank/projects/Zubarev_sponge/Analysis/2024_05_18_Seurat_clean/UMAP_annotated.pdf', height=5, width=9)
DimPlot(HDuj_all, group.by = "cell_type", repel=TRUE, label=TRUE, label.size = 3)
dev.off()
```

Save objects with cell types annotated

```{r}
HDuj_all[["RNA3"]] <- as(object = HDuj_all[["RNA"]], Class = "Assay")
DefaultAssay(HDuj_all) <- "RNA3"
HDuj_all[["RNA"]] <- NULL
HDuj_all <- RenameAssays(object = HDuj_all, RNA3 = 'RNA')
SaveH5Seurat(HDuj_all, filename = "/tank/projects/Zubarev_sponge/Analysis/2024_05_18_Seurat_clean/HDuj_annotated_celltypes_20240523.h5Seurat")
Convert("/tank/projects/Zubarev_sponge/Analysis/2024_05_18_Seurat_clean/HDuj_annotated_celltypes_20240523.h5Seurat", dest="h5ad")
```
